---
title: "UpAndInPutOption"
output: html_document
date: "2024-02-29"
---

```{r }
##install.packages("UpInPutEurOption_1.1.0.tar.gz",
 ##           type = "binaries",
 ##                repos = NULL)
library(tidyverse)
```

### Variables
```{r }
nInt = 1000
strike= 150
spot= 140
vol=0.24
Rfr= 0.07
expiry= 0.75
br = 20
nReps=1000

```


```{r }
UpInPutEurOption::getPriceForEuropeanUpAndInPut(nInt, strike, spot, vol, Rfr, expiry, br, nReps)

```

```{r }
getMCEuropeanPutExpiry <- function (expiry) {
  return(
    UpInPutEurOption::getPriceForEuropeanUpAndInPut(nInt, strike, spot, vol, Rfr, expiry, br, nReps)
    )
}
expiry <- seq(0.01, 0.71, by = 0.01)
prices <- sapply(expiry, getMCEuropeanPutExpiry)
```


```{r}

tibble( expiry, prices) %>%
  ggplot(aes(expiry, prices)) +
  geom_point(col = "blue") +
  labs(
    x     = "time to maturity",
    y     = "option price",
    title = "price of Put Up-IN option with a barrier  vs. time  to maturity")

```

### ============== 2. build an R wrapping function: option price vs. spot and volatility ===================================

```{r }
getMCEuropeanPutSpotAndvol <- function (spot, vol) {
  return(
   UpInPutEurOption::getPriceForEuropeanUpAndInPut(nInt, strike, spot, vol, Rfr, expiry, br, nReps))
}

# sequences of argument values
spot <- seq(70, 110, by = 1)
vol  <- c(0.001, 0.01, 0.02, 0.05, 0.1, 0.15, 0.2, 0.24)
expiry= 0.75
grid      <- expand.grid(spot = spot, vol = vol)
prices    <- mapply(getMCEuropeanPutSpotAndvol,
                    spot = grid$spot, vol = grid$vol)
```

#============== ==============  visualization: options price vs. spot price and volatility ============== ============== 
```{r }
grid %>%
  as_tibble() %>%
  bind_cols(price = prices) %>%
  ggplot(aes(x = spot, y = price, group = vol, colour = vol)) +
  geom_line() +
  geom_point(size = 1, shape = 21, fill = "white") +
  labs(
    x     = "spot price",
    y     = "option price",
    title = "price Put up-In option with a barrier  vs  volatility")
```


#### Objective
The Goal of the Project is to apply Up-In Put European with Barrier


#### Assumptions  
1-Time Value: The option's value increases with time, reflecting the time value of options. This is because as maturity increases, there are more chances for the option to become "in-the-money" due to price fluctuations.

2-Volatility Impact: Higher volatility increases the option's value, which is typical for options as greater volatility means a higher probability of the option breaching the barrier and becoming active.

3-Non-Linear Time Decay: The non-linear increase in the option price with time suggests that the time decay (theta) of the option is not constant and could accelerate as the option nears expiration.

4-Inverse Spot Price Relationship: The option price decreases as the spot price increases, which is characteristic of put options, since they become more valuable as the underlying asset's price decreases.

#### Results

1-The first graph shows a relationship between the price of an up-and-in put option and the time to maturity. As the time to maturity increases, the option price generally increases, indicating that time has a positive impact on the value of the option.

2-In the first graph, the increase in option price is not linear; it shows some level of curvature, suggesting that the rate of increase in option price changes as the time to maturity lengthens.

3-The second graph illustrates the relationship between the price of an up-and-in put option with a barrier and the underlying spot price across different levels of volatility. The option price decreases as the spot price increases.

4-In the second graph, the impact of volatility is shown by different shades, with darker lines representing higher volatility. Higher volatility levels lead to a steeper slope, indicating that the option price is more sensitive to changes in the spot price when volatility is higher.

5-Additionally, the second graph demonstrates that the option price is inversely related to the spot price, and this relationship is consistent across different levels of volatility, albeit the price sensitivity changes.


#### In accordance with the Honor Code, I certify that my answers here are my own work, and I  did not make my solutions available to anyone else.




